MULTI EPOCH SPATIALLY RESOLVED RADIO OBSERVATIONS OF BETELGEUSE'S WIND ACCELERATION REGION

### 2014-06-29 draft1/ms.tex
comit from chalmers

\begin{abstract}
We present multi-epoch spatially resolved radio continuum observations of Betelgeuse at various combinations of wavelengths between $0.7-20.5$\,cm.  We used the Very Large Array (VLA) in the A configuration with the Pie Town Very Long Baseline Array (VLBA) antenna to fully resolved its atmosphere at 0.7, 1.3, 2.0, and 6.0\,cm at all epochs, and provide flux measurements at 20.5\,cm.

@@

\section{INTRODUCTION}
Red supergiants (RSGs) lose mass to the interstellar medium in the form of a massive ($\dot{M} \sim 10^{-7} - 10^{-4}\,M_{\odot}\,\rm{yr}^{-1}$) cool wind, with terminal velocities ($10\lesssim v_{\infty}\lesssim 50\,{\rm{km}}\,\rm{s}^{-1}$) typically less than the photospheric escape velocity  ($v_{\rm{esc}} \sim 100\,\rm{km},\rm{s}^{-1}$). These winds are major contributors of heavy elements to the interstellar medium (ISM) and play a crucial role in stellar evolution \citep{chiosi_1986}, and also in explaining the frequency of supernovae in the galaxy \citep[e.g.,][]{van_loon_2010}. Despite their importance, the mechanisms responsible for the formation of these winds in late K and early M-type RSGs remain largely unknown. Dust is observed too far from the star to play a significant role in the mass-loss process \citep{danchi_1994} and pulsation amplitudes are too low to initiate the mass-loss \citep{smith_1989}. Magnetohydrodynamic (MHD) waves \citep[e.g.,][]{thirumalai_2012} and large convective cells \citep[e.g.,][]{josselin_2007} have been proposed as alternative potential mass-loss mechanisms in RSGs but spatially resolved multi-epoch observations of RSGs are required to test these competing theories.

@@

\cite{lim_1998} used the VLA in its most extended (i.e., A) configuration to resolve Betelgeuse's atmosphere at 0.7\,cm and partially resolve it at 1.3, 2.0, 3.6, and 6\,cm. Because the radio emission is thermal and optically thick, they were able to calculate the mean gas temperature as a function of radius. They discovered that the mean gas temperature never reached chromospheric values (i.e., $\gtrsim 5000\,$K) and decreased steadily from $\sim$3450\,K at 2\,R$_{\star}$, to $\sim$1370\,K at 7\,R$_{\star}$. They also detected an asymmetry in their 0.7\,cm image which they attributed to the action of a large convective cell. To reconcile their results with the extended ultraviolet observations, which probed the same regions, they concluded that the inner atmosphere must be inhomogeneous to accommodate the hot chromospheric plasma, but that the cooler gas must be 3 orders of magnitude more abundant. \cite{harper_2006} used observations of the chromospheric tracer C II] $\lambda 2325\,$\AA to confirm this low filling factor for the chromospheric gas.

@@

\section{OBSERVATIONS AND DATA REDUCTION}
Betelgeuse was observed with the NRAO\footnote{The National Radio Astronomy Observatory is a facility of
the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} VLA  in the A configuration with the Pie Town (PT) Very Long Baseline Array (VLBA) antenna at multiple epochs between December 2000 and October 2004. The PT antenna is located 50\,km from the center of the VLA, and its inclusion to the A configuration improves the east-west resolution by a factor of 2. Our observations are summarized in the first two columns of Table \ref{tab1}. Our two multi-wavelength data sets in 2002 (Program: AH0778) were taken only $\sim 2$ months apart and consist of all wavelength bands between 1.3 and 20.5\,cm. We observed the star again under program AH0824 in 2003 and 2004 at all wavelength bands between 0.7 and 20.5\,cm. We also obtained VLA A configuration plus PT antenna data from the NRAO data archive (Program: AL0525) at  0.7 and 1.3\,cm which were taken in late 2000 and early 2001, respectively.

We used the ``fast switching'' phase calibration technique at 0.7 and 1.3\,cm to compensate for tropospheric phase variations. This allowed us to switch between observations of the point source phase calibrator 0532+075 and Betelgeusese, with cycle times of 140 and 160\,s at 0.7 and 1.3\,cm, respectively. The archival data from 2000/2001 also implemented the fast switching technique at these wavelengths but used the point source phase calibrator 0552+032, which was $\sim 10$ times more faint at these wavelengths but 1.5$^{\circ}$ closer to Betelgeuse. We again used interleaving observations of 0532+075 to calibrate phase variations at longer wavelengths, but implemented longer cycle times of between $12-15$\,min. Absolute flux calibration was obtained from 3C\,48 at 6.1\,cm, and 3C\,286 at all other wavelengths. The raw visibilities were flagged and calibrated according to standard VLA continuum data reduction procedures using the Astronomical Image Processing System \cite[AIPS;][]{greisen_1990}. The calibrated visibilities were imaged in both AIPS and the Common Astronomical Software Application  \cite[CASA;][]{mcmullin_2007} package.

@@

\tablecaption{Multi Epoch VLA A-Configuration Plus Pie Town Link Observations of Betelgeuse.}

@@

		 2004 Oct 21,30  & 0.7 & $39\times 26$ & 0.37	& $99\pm 3$ & $0.93\pm 0.04$& $92\pm 20$ &$28.67\pm 0.53$ & $2940\pm 170$\\
		 				 & 1.3 & $80\times 42$ & 0.09   & $121\pm 2$& $\dots$ & $\dots$& $13.88\pm 0.10$& $3140\pm 80$\\
						 & 2.0 & $121\times 91$ & 0.08  & $158\pm 6$& $\dots$ & $\dots$ & $7.23\pm 0.15$& $2270\pm 130$ \\
						 & 3.6 & $208\times 126$ & 0.02	& $215\pm 7$& $0.87\pm 0.04$ & $162\pm 7$& $3.34\pm 0.03$& $2110\pm 110$\\
						 & 6.1 & $377\times 264$ & 0.02	& $315\pm 30$& $0.59\pm 0.13$ & $173\pm 10$ & $1.55\pm 0.04$& $1140\pm 160$\\
						 & 20.5& $1262\times 889$ & 0.03& $\le 889$ & $\dots$ & $\dots$ &$0.25\pm 0.03$ &$ \textgreater 260$\\

@@

\rule{-2.6pt}{2.5ex}  2003 Aug 10,12 & 0.7 		& $40\times 27$ & 0.46	& $103\pm 4$& $0.89\pm 0.06$ & $104\pm 16$& $28.05\pm 0.84$& $2760\pm 230$ \\
									 & 1.3		& $80\times 42$ & 0.17	& $122\pm 5$& $\dots$& $\dots$& $11.20\pm 0.24$& $2490\pm 150$\\
									 & 2.0		& $119\times 96$& 0.10	& $132\pm 10$& $0.87\pm 0.10$& $11\pm 27$& $5.88\pm 0.17$&$3040\pm 360$\\
									 & 3.6		& $ 204\times 139$&	0.03& $193\pm 7$& $0.73\pm 0.06$ & $152\pm 7$& $2.80\pm 0.04$&  $2610\pm 170$\\
									 & 6.1 		& $378\times 297$&	0.03& $209\pm 49$& $\dots$ & $\dots$& $1.22\pm 0.04$&$2040\pm 680$ \\
					                 &20.5		& $1247\times 931$&0.04	& $\le 931$& $\dots$ & $\dots$& $0.26\pm 0.03$& $ \textgreater 250$\\

@@

\rule{-2.6pt}{2.5ex}  2002 Apr 12,13  & 1.3 		& $91\times 59$ & 0.18	&$134\pm 9$ & $0.76 \pm 0.07$& $36\pm 10$& $8.96\pm 0.24$& $2170\pm 250$\\
							& 2.0		&$131\times 98$ & 0.39	& $166\pm 16$& $0.63\pm 0.10$&$41\pm 11$ & $5.32\pm 0.23$& $2420\pm 450$ \\
							& 3.6		& $224\times 155$&0.03	& $234\pm 9$& $0.73\pm 0.05$& $40\pm7$& $2.66\pm 0.04$& $1690\pm 110$\\
							& 20.5	& $1398\times 1146$& 0.06	& $\le 1146$ & $\dots$ & $\dots$& $0.38\pm 0.06$& $ \textgreater 240$\\

@@

\tablenotetext{}{Notes.- The restoring beam and image rms noise values were obtained using uniform weighting and include the Pie Town antenna baselines. The position angles (measured in degrees east of north) of the restoring beams in these images are not given here but are all between $30^{\circ}$ and $70^{\circ}$. The major axis of the stellar radio disk, $\theta _{\mathrm{maj}}$, the axis ratio of the major and minor radio disks, $\theta _{\mathrm{maj}}/\theta _{\mathrm{min}}$, the position angle, P.A., and the total flux density, $F_{\nu}$, are all derived from the best-fit uniform-brightness ($T_b$) elliptical-disk models.}

@@

\subsection{Imaging}
The calibrated visibilities at all wavelengths were imaged using CASA's \textit{clean} task while applying uniform weighting. With uniform weighting, each visibility is given a weight that is inversely proportional to the sampling density function. This optimises the full resolution of the array and minimises the sidelobe level. However, it also leads to an increase in the image noise level in comparison to natural weighting, which gives a constant weight to all visibilities, and Briggs weighting, which is a compromise between uniform and natural. Additional images were also created at 0.7 and 1.3\,cm which implemented both Briggs weighting, and natural weighting with a restoring beam size corresponding to that obtained using uniform weighting, as used in \cite{lim_1998}. These additional images were used to check if asymmetries produced by one weighting scheme could be reproduced by another.

@@

\section{RESULTS} 
\subsection{Radio Maps} 
\begin{figure*}
\mbox{
\includegraphics[trim = 30mm 90mm 50mm 80mm, clip,scale=0.55]{/home/eamon/pietown/paper/figs/nature_fig.ps}
\includegraphics[trim = 0mm 50mm 20mm 58mm, clip,scale=0.4,angle=90]{/home/eamon/pietown/paper/figs/vla_q_2000.ps}
\includegraphics[trim = 0mm 0mm 20mm 58mm, clip,scale=0.40,angle=90]{/home/eamon/pietown/paper/figs/vla_q_2004.ps}
}
\caption{VLA A-configuration maps of Betelgeuse at 0.7\,cm. }
\label{fig:fig5}
\end{figure*}
The resulting restoring beam sizes and image rms noise levels are given in columns 3 and 4 of Table \ref{tab1}.

Problem with C band data

threw away Q band pie town baselines, compare to lim, one component even at the highest frequencies unlike emerlin image, no non-axially symmetry let alone hotspots.
\subsection{Diameters} 
Importance of working in the visibility domain
Previous VLA observations have only spatially resolved the stellar atmosphere at 0.7\,cm but here we fully resolve the star at all wavelengths between 0.7 and 6.1\,cm. Skinner discussion
Point to Table 1 give diameter variability.
\subsection{Flux Densities}
obtained from visibilty fits but also checked against elliptical Gaussian fitted results
plot flux versus frequency (see harper paris presentation)
\subsection{Temperature Profiles}
give more exact lim formula

\section{DISCUSSION}
\subsection{Radio Flux Density Variability} 
see Reid \& Menton 1996 conf proceedings\\
see Drake conf proceedings\\
e-MERLIN flux is concentrated\\
see Harper\_variability. ps\\
does flux go up as ang diam go up

@@

\acknowledgments
The data presented in this paper were obtained with the Karl G. Jansky Very Large Array (VLA) which is an instrument of the National Radio Astronomy Observatory (NRAO). The NRAO is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc. We wish to thank the NRAO helpdesk for their detailed responses to our CASA related queries. This publication has emanated from research conducted with the financial support of Science Foundation Ireland under Grant Number SFI11/RFP.1/AST/3064, and a grant from Trinity College Dublin.

>>>>

\begin{abstract}
We present multi-epoch spatially resolved radio continuum observations of Betelgeuse at various combinations of wavelengths between $0.7-20.5$\,cm.  We used the Very Large Array (VLA) in the A configuration with the Pie Town (PT) Very Long Baseline Array (VLBA) antenna to fully resolved its atmosphere at 0.7, 1.3, 2.0, and 6.0\,cm at all epochs, and provide flux measurements at 20.5\,cm.

Our low-frequency observations confirm the multiple outburst interpretation of the spectral index differences at high frequencies.

@@

\section{INTRODUCTION}
Red supergiants (RSGs) lose mass to the interstellar medium in the form of a massive ($\dot{M} \sim 10^{-7} - 10^{-4}\,M_{\odot}\,\rm{yr}^{-1}$) cool wind, with terminal velocities ($10\lesssim v_{\infty}\lesssim 50\,{\rm{km}}\,\rm{s}^{-1}$) typically less than the photospheric escape velocity  ($v_{\rm{esc}} \sim 100\,\rm{km}\,\rm{s}^{-1}$). These winds are major contributors of heavy elements to the interstellar medium (ISM) and play a crucial role in stellar evolution \citep{chiosi_1986}, and also in explaining the frequency of supernovae in the galaxy \citep[e.g.,][]{van_loon_2010}. Despite their importance, the mechanisms responsible for the formation of these winds in late K and early M-type RSGs remain largely unknown. Dust is observed too far from the star to play a significant role in the mass-loss process \citep{danchi_1994} and pulsation amplitudes are too low to initiate the mass-loss \citep{smith_1989}. Magnetohydrodynamic (MHD) waves \citep[e.g.,][]{thirumalai_2012} and large convective cells \citep[e.g.,][]{josselin_2007} have been proposed as alternative potential mass-loss mechanisms in RSGs but spatially resolved multi-epoch observations of RSGs are required to test these competing theories.

@@

\cite{lim_1998} used the VLA in its most extended (i.e., A) configuration to resolve Betelgeuse's atmosphere at 0.7\,cm and partially resolve it at 1.3, 2.0, 3.6, and 6\,cm. Because the radio emission is thermal and optically thick, they were able to calculate the mean gas temperature as a function of radius and discovered that the mean gas temperature never reached chromospheric values (i.e., $\gtrsim 5000\,$K) but decreased steadily from $\sim$3450\,K at 2\,R$_{\star}$, to $\sim$1370\,K at 7\,R$_{\star}$. They also detected an asymmetry in their 0.7\,cm image which they attributed to the action of a large convective cell. To reconcile their results with the extended ultraviolet observations, which probed the same regions, they concluded that the inner atmosphere must be inhomogeneous to accommodate the hot chromospheric plasma, but that the cooler gas must be 3 orders of magnitude more abundant. \cite{harper_2006} used observations of the chromospheric tracer C II] $\lambda 2325\,$\AA to confirm this low filling factor for the chromospheric gas.

@@

\section{OBSERVATIONS AND DATA REDUCTION} 
Betelgeuse was observed with the NRAO\footnote{The National Radio Astronomy Observatory is a facility of
the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} VLA  in the A configuration with the Pie Town (PT) Very Long Baseline Array (VLBA) antenna at multiple epochs between December 2000 and October 2004. The PT antenna is located 50\,km from the center of the VLA, and its inclusion to the A configuration enhances the east-west resolution by a factor of 2. Our observations are summarized in the first two columns of Table \ref{tab1}. Our two multi-wavelength data sets in 2002 (Program: AH0778) were taken only $\sim 2$ months apart and consist of all wavelength bands between 1.3 and 20.5\,cm. We observed the star again under program AH0824 in 2003 and 2004 at all wavelength bands between 0.7 and 20.5\,cm. We also obtained VLA A configuration plus PT antenna data from the NRAO data archive (Program: AL0525) at  0.7 and 1.3\,cm which were taken in late 2000 and early 2001, respectively.

We used the ``fast switching'' phase calibration technique at 0.7 and 1.3\,cm to compensate for tropospheric phase variations. This allowed us to switch between observations of the point source phase calibrator 0532+075 and Betelgeusese, with cycle times of $2-3$\,min at 0.7, 1.3 and 2.0\,cm. The archival data from 2000/2001 also implemented the fast switching technique at these wavelengths but used the point source phase calibrator 0552+032, which was $\sim 10$ times more faint at 0.7\,cm but 1.4$^{\circ}$ closer to Betelgeuse. We again used interleaving observations of 0532+075 to calibrate phase variations at longer wavelengths, but implemented longer cycle times of $10-20$\,min. Absolute flux calibration was obtained from 3C\,48 at 6.1\,cm, and 3C\,286 at all other wavelengths. The absolute flux density uncertainty is estimated to range from 5\% to 10\% between the longest to shortest wavelengths, respectively. The flux density error values quoted in the remainder of this paper do not include this systematic error but represent the $\pm 1\sigma$ value. The raw visibilities were flagged and calibrated according to standard VLA continuum data reduction procedures using the Astronomical Image Processing System \cite[AIPS;][]{greisen_1990}. The calibrated visibilities were imaged in both AIPS and the Common Astronomical Software Application  \cite[CASA;][]{mcmullin_2007} package.

@@

\tablecaption{Multi Epoch VLA A Configuration Plus PT Link Observations of Betelgeuse.}

@@

		 2004 Oct 21,30  & 0.7 & $39\times 26$ & 0.37	& $99\pm 3$ & $92 \pm 20 $& $92\pm 20$ &$28.68\pm 0.53$ & $2940\pm 170$\\
		 				 & 1.3 & $80\times 42$ & 0.09   & $127\pm 2$& $ 114\pm 4$ & $85\pm 5$& $13.83\pm 0.10$& $3140\pm 80$\\
						 & 2.0 & $121\times 91$ & 0.08  & $158\pm 6$& $ 152\pm 17$ & $132\pm 59$ & $7.23\pm 0.15$& $2270\pm 130$ \\
						 & 3.6 & $208\times 126$ & 0.02	& $215\pm 7$& $188\pm 15$ & $0\pm 10$& $3.34\pm 0.03$& $2110\pm 110$\\
						 & 6.1 & $377\times 264$ & 0.02	& $314\pm 30$& $204\pm 54$ & $0\pm 20$ & $1.55\pm 0.04$& $1140\pm 160$\\
						 & 20.5& $1262\times 889$ & 0.03& $< 889$ & $< 889$ & $\dots$ &$0.25\pm 0.03$ &$ \textgreater 260$\\

@@

\rule{-2.6pt}{2.5ex}  2003 Aug 10,12 & 0.7 		& $40\times 27$ & 0.46	& $103\pm 4$& $92\pm 10$ & $104\pm 16$& $28.05\pm 0.84$& $2760\pm 230$ \\
									 & 1.3		& $80\times 42$ & 0.17	& $122\pm 5$& $115\pm 12$& $0\pm 5$& $11.20\pm 0.24$& $2490\pm 150$\\
									 & 2.0		& $119\times 96$& 0.10	& $132\pm 10$& $ 116\pm 22$& $11\pm 27$& $5.88\pm 0.17$&$3040\pm 360$\\
									 & 3.6		& $ 204\times 139$&	0.03& $193\pm 7$& $ 141\pm 17$ & $152\pm 7$& $2.80\pm 0.04$&  $2610\pm 170$\\
									 & 6.1 		& $378\times 297$&	0.03& $247\pm 47$& $180\pm 103$ & $169\pm 28$& $1.22\pm 0.04$&$2040\pm 680$ \\
					                 &20.5		& $1247\times 931$&0.04	& $< 931$& $< 931$ & $\dots$& $0.26\pm 0.03$& $ \textgreater 250$\\

@@

\rule{-2.6pt}{2.5ex}  2002 Apr 12,13  & 1.3 		& $91\times 59$ & 0.18	&$134\pm 9$ & $102\pm 16$& $36\pm 10$& $8.96\pm 0.24$& $2170\pm 250$\\
							& 2.0		&$131\times 98$ & 0.39	& $166\pm 16$& $105\pm 27$&$41\pm 11$ & $5.32\pm 0.24$& $2420\pm 450$ \\
							& 3.6		& $224\times 155$&0.03	& $234\pm 9$& $171\pm 18$& $41\pm7$& $2.66\pm 0.04$& $1690\pm 110$\\
							& 20.5	& $1398\times 1146$& 0.06	& $< 1146$ & $< 1146$ & $\dots$& $0.38\pm 0.06$& $ \textgreater 240$\\

@@

\tablenotetext{}{Notes.- The restoring beam sizes and image rms noise values are taken from the uniformly weighted radio maps that include the PT antenna baselines. The position angles (measured in degrees east of north) of the restoring beams are not quoted here, but are all between $30^{\circ}$ and $70^{\circ}$. The major and minor axis of the stellar radio disk $\theta _{\mathrm{maj}}$ and $\theta _{\mathrm{min}}$, the position angle P.A., and the total flux density $F_{\nu}$, are all derived from the best-fit uniform-brightness ($T_b$) elliptical-disk models.}

@@

\subsection{Imaging}\label{obs2.1}
The calibrated visibilities at all wavelengths were imaged using CASA's \textit{clean} task while applying uniform weighting. With uniform weighting, each visibility is given a weight that is inversely proportional to the sampling density function. This optimises the full resolution of the array and minimises the sidelobe level. However, it also leads to an increase in the image noise level in comparison to natural weighting, which gives a constant weight to all visibilities, and Briggs weighting, which is a compromise between uniform and natural weighting. Additional images were also created at 0.7 and 1.3\,cm which implemented both Briggs weighting, and natural weighting with a restoring beam size equal to that obtained using uniform weighting, as used in \cite{lim_1998}. These additional images were used to check if asymmetries produced by one weighting scheme could be reproduced by another.

@@

\section{RESULTS} 
\subsection{Radio Maps}
Radio maps were produced at all wavelengths using uniform weighting to utilize the full capabilities of the PT baselines and achieve maximum spatial resolution. The corresponding restoring beam sizes and image rms noise levels are provided in columns 3 and 4 of Table \ref{tab1}. Calibrations issues with the two 6.1\,cm data sets from 2002 resulted in rms noise values being ~10 times higher than expected. This resulted in the source not being detected in the April 2002 map and the source being located $\sim 300$\,mas away from its expected position in the February 2002 map. We therefore do not include these 6.1\,cm results in Table \ref{tab1} and in any of the analysis.The remainder of the maps were generally of excellent quality with the source clearly resolved at the shorter wavelengths. No deviations from axially symmetry were present in any of the maps between 1.3 and 20.5\,cm.

All of the 0.7\,cm maps showed significant deviations from axial symmetry. However, when the data sets were imaged using the different weighting schemes described in Section \ref{obs2.1}, the morphology was inconsistent. For example, the maps created using standard uniform weighing were morphologically different to the maps created using natural weighting with a restoring beam of size corresponding to that produced with uniform weighting. These inconsistencies are probably due to poor phase stability resulting from rapid tropospheric phase fluctuations of which our cycle times were not short enough to compensate for. To investigate this further, we removed the PT antenna baselines and again imaged the data using the two aforementioned
imaging techniques. We found that two data sets (i.e., from 2000 and 2004) produced images that had consistent morphology when any of the imaging techniques were applied. The observing logs of the other data sets report poorer weather conditions in agreement with our imaging analysis. The resulting images are plotted in Figure \ref{fig1} along with the 0.7\,cm image from \cite{lim_1998} for comparison. In these data sets, the cycle time was adequate to obtain reasonable phase transfer from the calibrator to the source but shorter cycle times were probably required for the other data sets due to poorer weather. Unlike the \cite{lim_1998} map, no asymmetries are present in either of our two maps as is clearly evident in Figure \ref{fig1}. These maps indicate that large scale asymmetries are not always present in Betelgeuse's inner atmosphere.

\begin{figure*}
\mbox{
\includegraphics[trim = 6mm 0mm 0mm 0mm, clip,scale=0.95]{/home/eamon/pietown/paper/figs/fig1.ps}
%\includegraphics[trim = 30mm 90mm 50mm 80mm, clip,scale=0.55]{/home/eamon/pietown/paper/figs/nature_fig.ps}
%\includegraphics[trim = 0mm 50mm 20mm 58mm, clip,scale=0.4,angle=90]{/home/eamon/pietown/paper/figs/vla_q_2000.ps}
%\includegraphics[trim = 0mm 0mm 20mm 58mm, clip,scale=0.40,angle=90]{/home/eamon/pietown/paper/figs/vla_q_2004.ps}
}
\caption{VLA A configuration maps of Betelgeuse at 0.7\,cm over three different epochs. These maps have been created by naturally weighting the visibilities and using a restoring beam corresponding to the size created from uniform weighting. The restoring beam size and shape is located in the bottom left position of each panel while the red circle is the approximate location and size of the optical photosphere. From left to right the beam sizes are x, y, and z$\prime\prime$ and the rms noise values are x, y, and z\,mJy\,beam$^{-1}$. \textit{Left panel}: The \cite{lim_1998} map shows an asymmetry in the east direction. The position of the photosphere is here assumed to be .... \textit{Middle and right panels}: Our 0.7\,cm maps created without any visibilities from the PT baselines. No asymetries deviating from the restoring beam shape are present. The position of the photosphere is here assumed to be located on the peak emission.}
\label{fig1}
\end{figure*}

\subsection{Diameters} 
Importance of working in the visibility domain
Previous VLA observations have only spatially resolved the stellar atmosphere at 0.7\,cm but here we fully resolve the star at all wavelengths between 0.7 and 6.1\,cm. Skinner discussion
Point to Table 1 give diameter variability.

xaxis 'Real Visibility (mJy)' colour pietown baselines

Compare to Harper 2001 paper

\subsection{Flux Densities}
obtained from visibilty fits but also checked against elliptical Gaussian fitted results
plot flux versus frequency (see harper paris presentation)
\subsection{Temperature Profiles}
give more exact lim formula

\section{DISCUSSION}
\subsection{Radio Flux Density Variability} 
see Reid \& Menton 1996 conf proceedings\\
see Drake conf proceedings\\
e-MERLIN flux is concentrated\\
see Harper\_variability. ps\\
does flux go up as ang diam go up\\
see Harper 2001 discussion

@@

\acknowledgments
The data presented in this paper were obtained with the Karl G. Jansky Very Large Array (VLA) which is an instrument of the National Radio Astronomy Observatory (NRAO). The NRAO is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
